Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-15 paper/v2/paper-edited.tex
3

%Operators today generate the BGP configuration of individual devices based on intended policy.
When generating BGP configurations, whether fully manually or aided by templates, the operators face the challenge of decomposing network-wide policies
into appropriate device-level policies.
This decomposition is not always straightforward and ensuring policy-compliance is tricky, especially in the face of failures. We illustrate this point using two examples based on policies that we have seen in practice. The next section shows how \sysname allows operators to express these policies directly.
%the ease with which the
%policies can be specified using our new language \sysname.
%The next section describes how to automatically compile this specification to device-level policies.

@@

To implement P1 of the policy, the operators must compute and assign
local preferences such that preferences at \CD{Cust}-facing interfaces
$>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
the same time, to satisfy P3, the preference at \CD{R2}'s
\CD{Cust}-facing interface should be lower than that at
\CD{R1}. Implementing P3 properly will require MEDs to be appropriately configured on \CD{R1} and \CD{R2}.
To implement P2, the operators can assign communities that
indicate where a certain routing announcement entered the
network. Then, \CD{R4} must be configured to not announce to
$\CD{Peer}$ routes that have communities that correspond to the
\CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links. A similar policy must be configured for \CD{R2}. Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based import and export filters at each router.

Clearly it is difficult to properly configure even this
small example network manually; devising correct configurations for real networks can quickly become a nightmare. Such networks have many neighbors spanning multiple commercial-relationship classes, differing numbers of links to each neighbor, along with several neighbor- or prefix-based exceptions to the default behavior. A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually.
%\sysname lets operators express such policies easily and intuitively. It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.

@@

The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ announce what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}. This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be assigned to local services without updating router configurations).

However, this implementation does not have the right behavior in the face of failures. Suppose links X--G and X--H fail. Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D. Per policy implementation, X will start "leaking" these prefixes externally. Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are used for other services outside of the data center). This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter. A similar problem will happen if links Y--G and Y--H fail.
%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
Link failures in data centers are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.

To avoid this problem, the operator may decide to disallow "valley" paths, i.e., those that go up, down, and back up again. This guard can be implemented by $X$ and $Y$ rejecting paths through the other. But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{route-aggregation}. If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce \CD{PG} externally. This announcement will bring to X traffic for \CD{PG1} as well, but because of valley-free filtering, X does not have a valid route for \CD{PG1} and will thus drop all traffic to it.

Thus, we see that devising a configuration that ensures policy compliance in the face of failures is complex and error-prone. \sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures (if that is possible; otherwise, it generates a compile-time error). For aggregation, it also provides a lower bound to operators on the number of failures under which aggregation will not result in blackholes.

>>>>

%Operators today generate the BGP configuration of individual devices based on intended policy.
When generating BGP configurations, whether manually or aided by templates, the operators face the challenge of decomposing network-wide policies
into correct device-level policies.
This decomposition is not always straightforward and ensuring policy-compliance is tricky, especially in the face of failures. In this section, we illustrate this difficulty using two examples based on policies that we have seen in practice. The next section shows how \sysname allows operators to express these policies naturally.
%the ease with which the
%policies can be specified using our new language \sysname.
%The next section describes how to automatically compile this specification to device-level policies.

@@

To implement policy P1, the operators must compute and assign
local preferences such that preferences at \CD{Cust}-facing interfaces
$>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
the same time, to satisfy P3, the preference at \CD{R2}'s
\CD{Cust}-facing interface should be lower than that at
\CD{R1}. Implementing P3 will also require MEDs to be appropriately configured on \CD{R1} and \CD{R2}.
To implement P2, the operators can assign communities that
indicate where a certain routing announcement entered the
network. Then, \CD{R4} must be configured to not announce to
$\CD{Peer}$ routes that have communities that correspond to the
\CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links. A similar policy must be configured for \CD{R2}. Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based import and export filters at each router.

Clearly, it is difficult to correctly configure even this
small example network manually; correctly configuring real, larger networks can quickly become a nightmare. Such networks have hundreds of neighbors spanning multiple commercial-relationship classes, differing numbers of links to each neighbor, along with several neighbor- or prefix-based exceptions to the default behavior. A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually.
%\sysname lets operators express such policies easily and intuitively. It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.

@@

The operator may implement the policy by having X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ export externally what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}. This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can occur independently, e.g., local services can be assigned new prefixes without updating those routers' configurations.

However, this implementation has incorrect behavior in the face of failures. Suppose links X--G and X--H fail. Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D. Per its policy implementation, X will start "leaking" these prefixes externally. Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are reused for other services outside of the data center). This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter. A similar problem will happen if links Y--G and Y--H fail.
%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
Link failures in data centers are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.

To avoid this problem, the operator may disallow "valley" paths, i.e., those that go up, down, and back up again. This guard can be implemented by $X$ and $Y$ rejecting paths through the other. But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{route-aggregation}. If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce \CD{PG} externally. This announcement will bring to X traffic for \CD{PG1} as well, but because valleys are disallowed, X does not have a valid route for \CD{PG1} and will drop all traffic to it.

Thus, we see that devising a configuration that ensures policy compliance in the face of failures is complex and error-prone. \sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures if possible---otherwise, it generates a compile-time error. For aggregation, it also provides a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
